---
title: "A doc with some parallax"
format: html
css: style.css
editor: visual
---

<br/><br/>

<div class="parallax-container"><div class="parallax-image-container"></div></div>

<br/><br/>

Let's start with some code

```{r, eval=FALSE}
#| fig-width: 3
#| fig-height: 3

# Load the ggplot2 package
library(ggplot2)

# Create a box plot using ggplot2
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot() + # Add box plot
  labs(x = "Number of Cylinders", y = "Miles per Gallon") + # Label axes
  ggtitle("Box Plot of MPG ")
```


Parallax is **the observed displacement of an object caused by the change of the observer's point of view**. 

In astronomy, it is an irreplaceable tool for calculating distances of far away stars. Parallax enables astronomers to measure the distances of far away stars by using trigonometry.

<br/><br/>

<div class="parallax-container"><div class="parallax-image-container"></div></div>

<br/><br/>

Parallax scrolling is also a web site trend where the background content (i.e. an image) is moved at a different speed than the foreground content while scrolling.

```{r}
#| fig-width: 3
#| fig-height: 3

# Load the ggplot2 package
library(ggplot2)

# Create a scatterplot using ggplot2
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point() + # Add points
  labs(x = "Miles per Gallon", y = "Weight") + # Label axes
  ggtitle("Scatterplot of MPG vs. Weight") # Add title

```

Note: this is possible thanks to the attached css style sheet!