---
title: "Crypto price analysis: `r params$crypto`"
format: html
params:
  crypto: "bitcoin"
toc: true
---

This report is gives some information about the `r params$crypto` price for the last 2 weeks.

It is also used to show how parametrized reports in Quarto work.

# Getting data

 The `r params$stockTicker` price can be fetched from the coingecko API. Here is the code to do so:

```{r, warning=F, message=F}
# Libraries
library(jsonlite)
library(tidyverse)

# Get today's date and the date 1 year ago
end_date <- as.integer(as.POSIXct(Sys.Date()))
start_date <- as.integer(as.POSIXct(Sys.Date() - 365))

# Construct the API URL
url <- paste0(
  "https://api.coingecko.com/api/v3/coins/",
  params$crypto,
  "/market_chart/range?vs_currency=usd&from=",
  start_date, "&to=", end_date
)

# Fetch the data using readLines
json_data <- readLines(url, warn = FALSE)

# Parse the JSON data
data <- fromJSON(json_data)$prices %>% as.data.frame()
colnames(data) <- c("timestamp", "value")

# Format the date (date is provided in millisecond, thus division by 1000)
data$timestamp <- date(data$timestamp / 1000)
```

# `r params$crypto` price evolution

Now, let's make a chart to show the evolution using dygraph:

```{r}
library(dygraphs)

dygraph(data)

```




# Conclustion

Read more about parametrized reporting in Quarto here.
